---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## NeuroSTR 
Is a library... It is documented at. 

## R interface to NeuroSTR   
Currently it provides a subset of functionalities. Say types are currently not exported

These are documented in original package documentation.

## Fature tools 
At level of node, branch, and **neurites**. 

The main thing is the output data frame. Yet, this data 

Their output and input. What changes is that you can also get it directly as a data frame, althought the objects are then not exactly identical. the options of the tools are reduced.  

The feature tools are  

```{r}
library(neurostr) 
```


## Pending 
Many options are not available directly. However, it is easy to do 

## Extending the output 
Merging node and branch level? These are primitives and many useful can be built on top of it.  
