---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## NeuroSTR 
NeuroSTR is a C++ neuroanatomy toolbox. It reads and processes three-dimensional neuron reconstructions in the most common file formats and offers a huge set of functions and utilities to work with them.  

It is documented at <https://computationalintelligencegroup.github.io/neurostr/>. 

## R interface to NeuroSTR   
The package currently provides a subset of functionalities, by providing wrappers to the following NeuroSTR [precompiled tools ](<https://computationalintelligencegroup.github.io/neurostr/doc/tools.html>):  

- Node Feature Extractor
- Branch Feature Extractor
- Format converter
- Neuron Validator  

**To do: docuemt node features**


## Fature tools 
The tool output json strings. So, to get branch level features, we run:   

```{r}
library(neurostr)  
file <- system.file("extdata", "C030397A-P2.swc", package = "neurostr") 
branch <- compute_branch_features(ifile = file, omitdend = TRUE)
head(branch)
```

The arguments are identical as to the tools, although there are some less options. 
At level of node, branch, and **neurites**.   The main thing is the output data frame. Yet, this data 
Their output and input. What changes is that you can also get it directly as a data frame, althought the objects are then not exactly identical. the options of the tools are reduced.   The feature tools are   These are documented in original package documentation.  

## Pending 
Many options are not available directly. However, it is easy to do 
Say types are currently not exported

## Extending the output 
Merging node and branch level? These are primitives and many useful can be built on top of it.  
