---
title: "neurostr: an R wrapper for the NeuroSTR neuroanatomy toolbox"
author: "Bojan Mihaljevic, Luis Rodriguez-Lujan"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## NeuroSTR 
NeuroSTR is a C++ neuroanatomy toolbox. It reads and processes three-dimensional neuron reconstructions in the most common file formats and offers a huge set of functions and utilities to work with them.  

It is documented at <https://computationalintelligencegroup.github.io/neurostr/>. 

## R interface to NeuroSTR   
The `neurostr` package currently provides a subset of functionalities, by providing wrappers to the following NeuroSTR [precompiled tools ](<https://computationalintelligencegroup.github.io/neurostr/doc/tools.html>) (the corresponding `neurostr` function in parenthesis):  

- Node Feature Extractor (`compute_node_features()`) 
- Branch Feature Extractor (`compute_branch_features`)
- Format converter (`convert()`)
- Neuron Validator  (`validate()`) 


## Example 
We will compute branch-level features. The tools output JSON string which we can convert to data frames for easy manipulation. Thus: 

```{r}
library(neurostr)  
file <- system.file("extdata", "C030397A-P2.swc", package = "neurostr") 
branch <- compute_branch_features(ifile = file, omitdend = TRUE)
branch <- json2dataframe(branch)
head(branch)
```

The arguments passed to the functions are a subset of those provided to the corresponding tool. See the documentation of the corresponding function and of the tool itself.  

Similarly for node features:
```{r}
node <- compute_node_features(file)
node <- json2dataframe(node)
head(node)
```

## Working with the output 
The data frame allows for easy summarizing the properties and filtering. While selector are not exported from NeuroSTR, it is easily filtered with straightforward R. 

```{r}
branch$is_pre_terminal <- as.logical(branch$is_pre_terminal)
nrow(subset(branch, is_pre_terminal)) 
```

Also, a number of convenience functions are provided. Instead of using `subset`, we can select axonal branches with: 
```{r}
axon <- filter_neurite(branch, axon = TRUE)
nrow(axon)
```


We can merge branch and node data, and, for example, easily summarize node metrics across branches. For example, we compute the mean node length of pre-terminal branches with: 

```{r} 
```  
```{r, warning=FALSE, message=FALSE} 
branch_node <- merge_branch_node(branch, node)
pre_terminal <- subset(branch_node, is_pre_terminal)
library(dplyr)
pre_terminal <- dplyr::group_by(branch_node, branch)
summarize(pre_terminal, mean(node_length))
```

## Future work  
Functionalities such as arbor simplifications are currently not available. **However, it is easy to do ..**  Say types are currently not exported 
